THE HERA DISH III : MEASURING ELEMENT CHROMATICITY WITH REFLECTOMETRY.

### 2016-09-13 DishReflectometry/Paper1_v3.tex
Added abstract and completed editing upto section 4

\author{
Nipanjana Patra\UCB\myemail,
Aaron~R.~Parsons\UCB,
Nithyanandan Thyagarajan\ASU,
David~R.~DeBoer\UCB,
Zaki~S.~Ali\UCB,
Cherie~K.~Day\UCB, 
Carina Cheng\UCB,
%Gilbert Hsyu\altaffilmark{2}, 
%Tsz Kuk Leung\altaffilmark{2}
}
%\altaffiltext{2}{To be inserted}}

\begin{abstract}
\end{abstract}

@@

Since it was first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
~\cite{furlanetto_et_al2006, morales_wyithe2010, pritchard_loeb2012}),
the technical path toward measuring this signal has been extremely challenging.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that are yet to be fully solved.  With noise temperatures dominated
by sky noise and foregrounds four to five orders of magnitude
brighter than the signal, 
sky-averaged 21~cm monopole experiments such as
EDGES; ~\citep{Bowman_et_al2010},
BIGHORNS; ~\citealt{2015PhDT........65V},
SARAS; ~\citep{Patra_et_al2015}, \citep{Patra_et_al2013} ,
SCIHI; ~\citep{2015PhDT........65V},
HYPERION; ~\citep{presley_et_al2015}
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; ~\citealt{XXX}),
the Murchison Widefield Array (MWA; ~\citealt{XXX}),
the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{XXX}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{XXX}),
and the future Square Kilometre Array (SKA; ~\citealt{XXX})
must furnish both their foreground suppression limits given their system performance at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

@@

\section{\textbf{Effects of multiple reflections on visibility and delay spectrum}}
The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER. Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed. 
The reflected signal illuminates the dish and most of it is reflected back into the space.
However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed.
Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.  Identical spurious visibilities could be resulted due to reflections internal to the system causing delay space distortion. Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum. 
In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum in detail. We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$. 
 \subsection{\textbf{Antenna Reception With Multiple Reflections}}
\label{sec:multiple}
To examine the performance of an antenna and feed in the presence of multiple reflections, we can think of the system as a screen at a distance $F$ from a feed (see Figure \ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.  The screen reflects a factor, $\Gamma_d$, of the voltage and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed. 
Additionally, however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
$n^{th}$ reflection may be written as:
\begin{eqnarray}
\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
\label{eq6}
\end{eqnarray}

@@

An accurate measurement of this quantity requires receiving $v_{sky}$ from a well calibrated, wideband source in the sky in the far field of the HERA antenna element with significant isotropic emission. While this condition is hard to achieve in practice, due to the reciprocity of the antenna performance in the transmission and reception mode, the right hand side of equation \ref{eq:Sigma} could be measured using the return loss measurement technique with a vector network analyzer (VNA). \\

@@

\begin{eqnarray}
\volt_{rec} & = &  \Gamma_f \volt_{trans} \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \Gamma_d\Gamma_f\dfngexp \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^2 \nonumber \\
&&  ....+ \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^n \nonumber \\
\label{eq8}
\end{eqnarray}
Therefore, 
\begin{equation}
{\volt_{rec}\over \volt_{trans} } = \Gamma_f + \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
\label{eq9}
\end{equation}
The VNA measures the quantity $\volt_{rec}/\volt_{trans}=s_{11}$ which is the voltage reflection coefficient of the HERA element.
The fundamental differences between the right hand side of equations \ref{eq:Sigma} and \ref{eq:s11} are the $n=0$ term and the multiplicative factor in front of the convergent series $\displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}$ that represents the contribution of the delayed voltage components at the VNA input, arising due to multiple signal reflections between the feed and the dish. Finally, writing $\volt_{rec}/\volt_{trans}=s_{11}$, equation \ref{eq:s11} can be written as,
\begin{equation}
s_{11} +\frac{(1+\Gamma_f)^2}{\Gamma_f}-\Gamma_f = \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
\label{eq10}
\end{equation}
Comparing to Eq. \ref{eq:Sigma} and we find that
\begin{eqnarray}
{\volt_{rec}\over \volt_{sky} } & = & (1+\Gamma_d)\left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right] \nonumber\\
 & = & \bmvolt(\thhat,\nu) \left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right]
\label{eq11}
\end{eqnarray}
When the feed return loss is measured separately, all the higher order terms of equation \ref{eq:s11} do not exist. In this case, $\Gamma_f = s_{11}^{f}$. Using this measurement and the VNA measurement of $s11$, the quantity $v_{rec}\over v_{sky}$ is estimated. \\
%
\indent From this, for a two element interferometer with identical antenna elements, the ratio of the received sky intensity to true sky intensity will be, 
\begin{eqnarray}
{I_{rec}\over I_{sky} } & = & \Bigg|{\volt_{rec}\over \volt_{sky} }\Bigg|^2 =  \beam(\thhat,\nu)\times \nonumber\\
             && \left[|1+\Gamma_f|^2 +  2\operatorname{Re}\left(\frac{\Gamma_f}{(1+\Gamma_f)}(s_{11} - \Gamma_f)\right)\right] + \nonumber\\ 
             &&  \left[ \frac{|\Gamma_f|^2}{|1+\Gamma_{f}|^2}|s_{11} - \Gamma_f|^2  \right]  \nonumber\\
\label{eq12}             
\end{eqnarray}

@@

Comparing equations \ref{eq:power_ratio} and \ref{eq2}, the cross power generated by $v_{1}$ and $v_{2}$ would have a spurious visibility response due to the mutual correlation between multiply reflected voltages represented by the second and the third term of the right hand side of equation \ref{eq:power_ratio}. In the ideal case, $\Gamma_{f}=0$, in which case equation \ref{eq:power_ratio} results in equation \ref{eq2}. The Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. 
In the delay domain, visibilities contributed to by any two voltage components from two antennas with no mutual delay will be located at the delay $\tau = 0$ whereas any two voltage components from two antennas having a mutual delay of $n\Delta \tau$ will be centred at $n\Delta \tau$. These will broaden the width of the delay spectrum, which ultimately interferes with the 21cm power spectrum detection.

@@

\section{Results}
Return loss measurements yields the instrument pass band response that would manifest in autocorrelation data of a single HERA element. Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.

The simultated and measureded return loss of the feed as well as the HERA element is shown in figure \ref{RL_mag_feed} and figure \ref{RL_mag_dish}. The measurements deviates from the simulated performance in one major aspect. While the return loss of the simulated structure shows two resonant peaks around 120 and $160~MHz$, the feed resonance occur at slightly higher frequencies. While the simulated response shows very wide resonant peaks, as expected from these dipole structures, the measured return loss of the feed has a narrow peak around its low frequency resonance. This feature somewhat dominates the fall off rate in the delay response of the system bandpass. The delay response of the feed alone is shown in figure \ref{ds_feed_on_dish_trans} along with the delay response of a HERA element in transmission mode. In the following sections, we compute the response of the HERA element in the receiving mode. 
\begin{figure}[ht]
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_mag_feed.png}
\end{minipage}
\vspace{0.1cm}
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_ph.png}
\end{minipage}
\caption{Magnitude and phase of the return loss of the feed as simulated and measured. While both the measurement and the simulation shows similar resonance around $120~MHz$, the simulation shows a better matching to a 50 Ohm transmission line compared to the measurements. The measurement also has some small scale fluctuation due to multiple reflection of the signal at the VNA input. }   
\label{RL_mag_feed}
\end{figure}

\begin{figure}[ht]
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_mag_dish.png}
\end{minipage}
\vspace{0.1cm}
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_ph.png}
\end{minipage}
\caption{Magnitude and phase of the return loss of the HERA element as simulated and measured. In this case, both measurement and simulation shows similar level of return loss across the band with marginally better return loss at the high frequency end of the band. }   
\label{RL_mag_dish}
\end{figure}

\begin{figure}       
\centering
\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_feed_on_dish_trans_recp.png}
\caption{Delay spectrum of the HERA feed (brown) estimated by taking the Fourier transform of the measured return loss of power at the feed output. The feed, when suspended on the dish results in a more complex return loss as shown in figure \ref{RL_mag_dish} and corresponding delay response is shown here in black. This figure shows the delay spectrum of the instrument in the as estimated from direct measurements of the return loss i.e, in the transmission mode of the antenna. }
\label{ds_feed_on_dish_trans}
\end{figure}

Figure \ref{RL_mag_dish} shows the measured return loss when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex. The measured return loss is much more complex than what is found from the simulation. The delay spectrum in the transmission mode is shown in \ref{ds_feed_on_dish_trans}. To estimate the delay spectrum of the dish-feed assembly i.e one single HERA element, this measurement is first corrected to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}. The corrected measurement is then Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{corrected_response}. Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution. A number of systematic effects as well as mathematical artfacts that are critical to this measurements and their effects on the corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.

>>>>

\author{
Nipanjana Patra\UCB\myemail,
Aaron~R.~Parsons\UCB,
David~R.~DeBoer\UCB,
Nithyanandan Thyagarajan\ASU,
Aaron  Ewall-Wice\altaffilmark{7},
Gilbert Hsyu\UCB, 
Tsz Kuk Leung\UCB,
James E. Aguirre\altaffilmark{10}, Paul  Alexander\altaffilmark{5}, Zaki S. Ali\altaffilmark{1}, Adam P. Beardsley\altaffilmark{2}, Gianni  Bernardi\altaffilmark{11, 13}, Judd D. Bowman\altaffilmark{2}, Richard F. Bradley\altaffilmark{8}, Chris L. Carilli\altaffilmark{9}, Carina  Cheng\altaffilmark{1}, Cherie~K.~Day\UCB, Eloy  de~Lera~Acedo\altaffilmark{5}, Joshua S. Dillon\altaffilmark{1}, , Gcobisa  Fadana\altaffilmark{13}, Nicolas  Fagnoni\altaffilmark{5}, Randall  Fritz\altaffilmark{13}, Steve R. Furlanetto\altaffilmark{4}, Brian  Glendenning\altaffilmark{9}, Bradley  Greig\altaffilmark{12}, Jasper  Grobbelaar\altaffilmark{13}, Bryna J. Hazelton\altaffilmark{14, 15}, Jacqueline N. Hewitt\altaffilmark{7}, Jack  Hickish\altaffilmark{1}, Daniel C. Jacobs\altaffilmark{2}, Austin  Julius\altaffilmark{13}, MacCalvin  Kariseb\altaffilmark{13}, Saul A. Kohn\altaffilmark{10}, Telalo  Lekalake\altaffilmark{13}, Adrian  Liu\altaffilmark{1, 16}, Anita  Loots\altaffilmark{13}, David  MacMahon\altaffilmark{1}, Lourence  Malan\altaffilmark{13}, Cresshim  Malgas\altaffilmark{13}, Matthys  Maree\altaffilmark{13}, Zachary  Martinot\altaffilmark{10}, Nathan  Mathison\altaffilmark{13}, Eunice  Matsetela\altaffilmark{13}, Andrei  Mesinger\altaffilmark{12}, Miguel F. Morales\altaffilmark{14}, Abraham R. Neben\altaffilmark{7},  Samantha  Pieterse\altaffilmark{13}, Jonathan C. Pober\altaffilmark{3}, Nima  Razavi-Ghods\altaffilmark{5}, Jon  Ringuette\altaffilmark{14}, James  Robnett\altaffilmark{9}, Kathryn  Rosie\altaffilmark{13}, Raddwine  Sell\altaffilmark{13}, Craig  Smith\altaffilmark{13}, Angelo  Syce\altaffilmark{13}, Max  Tegmark\altaffilmark{7}, Peter K.~G. Williams\altaffilmark{6}, Haoxuan  Zheng\altaffilmark{7}
}
%\altaffiltext{2}{To be inserted}}

%\author{ James E. Aguirre\altaffilmark{10}, Paul  Alexander\altaffilmark{5}, Zaki S. Ali\altaffilmark{1}, Adam P. Beardsley\altaffilmark{2}, Gianni  Bernardi\altaffilmark{11, 13}, Judd D. Bowman\altaffilmark{2}, Richard F. Bradley\altaffilmark{8}, Chris L. Carilli\altaffilmark{9}, Carina  Cheng\altaffilmark{1}, Eloy  de~Lera~Acedo\altaffilmark{5}, Joshua S. Dillon\altaffilmark{1}, , Gcobisa  Fadana\altaffilmark{13}, Nicolas  Fagnoni\altaffilmark{5}, Randall  Fritz\altaffilmark{13}, Steve R. Furlanetto\altaffilmark{4}, Brian  Glendenning\altaffilmark{9}, Bradley  Greig\altaffilmark{12}, Jasper  Grobbelaar\altaffilmark{13}, Bryna J. Hazelton\altaffilmark{14, 15}, Jacqueline N. Hewitt\altaffilmark{7}, Jack  Hickish\altaffilmark{1}, Daniel C. Jacobs\altaffilmark{2}, Austin  Julius\altaffilmark{13}, MacCalvin  Kariseb\altaffilmark{13}, Saul A. Kohn\altaffilmark{10}, Telalo  Lekalake\altaffilmark{13}, Adrian  Liu\altaffilmark{1, 16}, Anita  Loots\altaffilmark{13}, David  MacMahon\altaffilmark{1}, Lourence  Malan\altaffilmark{13}, Cresshim  Malgas\altaffilmark{13}, Matthys  Maree\altaffilmark{13}, Zachary  Martinot\altaffilmark{10}, Nathan  Mathison\altaffilmark{13}, Eunice  Matsetela\altaffilmark{13}, Andrei  Mesinger\altaffilmark{12}, Miguel F. Morales\altaffilmark{14}, Abraham R. Neben\altaffilmark{7},  Samantha  Pieterse\altaffilmark{13}, Jonathan C. Pober\altaffilmark{3}, Nima  Razavi-Ghods\altaffilmark{5}, Jon  Ringuette\altaffilmark{14}, James  Robnett\altaffilmark{9}, Kathryn  Rosie\altaffilmark{13}, Raddwine  Sell\altaffilmark{13}, Craig  Smith\altaffilmark{13}, Angelo  Syce\altaffilmark{13}, Max  Tegmark\altaffilmark{7}, Nithyanandan  Thyagarajan\altaffilmark{2}, Peter K.~G. Williams\altaffilmark{6}, Haoxuan  Zheng\altaffilmark{7}}
%\affil{HERA Collaboration}
\altaffiltext{1}{Department of Astronomy, University of California, Berkeley, CA}
\altaffiltext{2}{School of Earth and Space Exploration, Arizona State University, Tempe, AZ}
\altaffiltext{3}{Physics Department, Brown University, Providence, RI}
\altaffiltext{4}{Department of Physics and Astronomy, University of California, Los Angeles, CA}
\altaffiltext{5}{Cavendish Astrophysics, University of Cambridge, Cambridge, UK}
\altaffiltext{6}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA}
\altaffiltext{7}{Department of Physics, Massachusetts Institute of Technology, Cambridge, MA}
\altaffiltext{8}{National Radio Astronomy Observatory, Charlottesville, VA}
\altaffiltext{9}{National Radio Astronomy Observatory, Socorro, NM}
\altaffiltext{10}{Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA}
\altaffiltext{11}{Department of Physics and Electronics, Rhodes University, PO Box 94, Grahamstown, 6140, South Africa}
\altaffiltext{12}{Scuola Normale Superiore, Pisa, Italy}
\altaffiltext{13}{SKA-SA, Cape Town, South Africa}
\altaffiltext{14}{Department of Physics, University of Washington, Seattle, WA}
\altaffiltext{15}{eScience Institute, University of Washington, Seattle, WA}
\altaffiltext{16}{Hubble Fellow}

\begin{abstract}
Spectral structure of the systematics has so far been the most dominant limiting factor for the experiments attempting to detect the redshifted 21~cm signal from the Epoch of Reionization (EoR). Systematics are specific to instruments and their direct measurement or estimation is not always straightforward. The Hydrogen Epoch of Reionization Array (HERA) uses the delay spectrum technique for estimating of 21~cm power spectrum. In a unique way, the delay spectrum technique directly translates to reflectometry in case of measuring instrumental response and allows the direct measurement of systematic effects in individual array element.  This paper presents a detailed investigation of the instrument chromaticity of an antenna element that constitute Hydrogen Epoch of Reionization Array. Reflectometry measurements are carried out on a HERA dish-feed assembly between 100 to 200~MHz which studies the multiple reflections in the system that finally results in various spurious spectral response in the measured visibility. Reflectometry measurements shows that even without incorporation of any sophisticated analysis method, the instrument is capable of measuring the line of sight component  of the $k$ mode          $k_{\parallel} >0.2 h Mpc^{-1}$ modes of power spectrum with very low foreground contaminations around $k_{\parallel} \approx0.2 h Mpc^{-1}$.  The performance is significantly better at the high frequency subbands of observation. When combined with a powerful foreground suppression method such as inverse covariance weighting, the instrument is capable of measuring the power spectrum for the spatial modes as low as $k_{\parallel} >0.1$. The study presented here qualifies HERA as a power spectrum instrument and serves as a fundamental method to design and measure instrument systematics for any future experiment that aims to detect the 21~cm EoR power spectrum.  
 \end{abstract}

@@

Since it was first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
~\cite{furlanetto_et_al2006, morales_wyithe2010, pritchard_loeb2012}),
the technical path toward measuring this signal has been extremely challenging.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that are yet to be fully solved.  With noise temperatures dominated
by sky noise and foregrounds four to five orders of magnitude
brighter than the signal, 
sky-averaged 21~cm monopole experiments such as
EDGES; ~\citep{Bowman_et_al2010},
BIGHORNS; ~\citealt{2015PhDT........65V},
SARAS; ~\citep{Patra_et_al2015}, \citep{Patra_et_al2013} ,
SCIHI; ~\citep{2015PhDT........65V},
HYPERION; ~\citep{presley_et_al2015}
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; ~\citealt{van_Haarlem_2013}),
the Murchison Widefield Array (MWA; ~\citealt{Tingay_2013}),
the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{Paciga_et_al2011}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{deBoer_2016}),
and the future Square Kilometre Array (SKA; ~\citealt{XXX})
must furnish both their foreground suppression limits given their system performance at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

@@

\section{\textbf{Effects of multiple reflections on visibility and delay spectrum}}
The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER. Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed. 
The reflected signal illuminates the dish and most of it is reflected back into the space.
However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed.
Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.  Identical spurious visibilities could be resulted due to reflections internal to the system causing delay space distortion. Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum. 
In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum in detail. We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$. 
 \subsection{Antenna Reception With Multiple Reflections}
\label{sec:multiple}
To examine the performance of an antenna and feed in the presence of multiple reflections, we can think of the system as a screen at a distance $F$ from a feed (see Figure \ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.  The screen reflects a factor, $\Gamma_d$, of the voltage and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed. 
Additionally, however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
$n^{th}$ reflection may be written as:
\begin{eqnarray}
\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
\label{eq6}
\end{eqnarray}

@@

An accurate measurement of this quantity requires receiving $v_{sky}$ from a well calibrated, wideband source in the sky in the far field of the HERA antenna element with significant isotropic emission. While this condition is hard to achieve in practice, due to the reciprocity of the antenna performance in the transmission and reception mode, the right hand side of equation \ref{eq7} could be measured using the return loss measurement technique with a vector network analyzer (VNA). \\

@@

\begin{eqnarray}
\volt_{rec} & = &  \Gamma_f \volt_{trans} \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \Gamma_d\Gamma_f\dfngexp \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^2 \nonumber \\
&&  ....+ \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^n \nonumber \\
\label{eq8}
\end{eqnarray}
Therefore, 
\begin{equation}
{\volt_{rec}\over \volt_{trans} } = \Gamma_f + \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
\label{eq9}
\end{equation}
The VNA measures the quantity $\volt_{rec}/\volt_{trans}=s_{11}$ which is the voltage reflection coefficient of the HERA element.
The fundamental differences between the right hand side of equations \ref{eq7} and \ref{eq9} are the $n=0$ term and the multiplicative factor in front of the convergent series $\displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}$ that represents the contribution of the delayed voltage components at the VNA input, arising due to multiple signal reflections between the feed and the dish. Finally, writing $\volt_{rec}/\volt_{trans}=s_{11}$, equation \ref{eq9} can be written as,
\begin{equation}
s_{11} +\frac{(1+\Gamma_f)^2}{\Gamma_f}-\Gamma_f = \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
\label{eq10}
\end{equation}
Comparing to Eq. \ref{eq7} we find that
\begin{eqnarray}
{\volt_{rec}\over \volt_{sky} } & = & (1+\Gamma_d)\left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right] \nonumber\\
 & = & \bmvolt(\thhat,\nu) \left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right]
\label{eq11}
\end{eqnarray}
When the feed return loss is measured separately, all the higher order terms of equation \ref{eq9} do not exist. In this case, $\Gamma_f = s_{11}^{f}$. Using this measurement and the VNA measurement of $s11$, the quantity $v_{rec}\over v_{sky}$ is estimated. \\
%
\indent From this, for a two element interferometer with identical antenna elements, the ratio of the received sky intensity to true sky intensity will be, 
\begin{eqnarray}
{I_{rec}\over I_{sky} } & = & \Bigg|{\volt_{rec}\over \volt_{sky} }\Bigg|^2 =  \beam(\thhat,\nu)\times \nonumber\\
             && \left[|1+\Gamma_f|^2 +  2\operatorname{Re}\left(\frac{\Gamma_f}{(1+\Gamma_f)}(s_{11} - \Gamma_f)\right)\right] + \nonumber\\ 
             &&  \left[ \frac{|\Gamma_f|^2}{|1+\Gamma_{f}|^2}|s_{11} - \Gamma_f|^2  \right]  \nonumber\\
\label{eq12}             
\end{eqnarray}

@@

Comparing equations \ref{eq13} and \ref{eq2}, the cross power generated by $v_{1}$ and $v_{2}$ would have a spurious visibility response due to the mutual correlation between multiply reflected voltages represented by the second and the third term of the right hand side of equation \ref{eq13}. In the ideal case, $\Gamma_{f}=0$, in which case equation \ref{eq13} results in equation \ref{eq2}. The Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. 
In the delay domain, visibilities contributed to by any two voltage components from two antennas with no mutual delay will be located at the delay $\tau = 0$ whereas any two voltage components from two antennas having a mutual delay of $n\Delta \tau$ will be centred at $n\Delta \tau$. These will broaden the width of the delay spectrum, which ultimately interferes with the 21cm power spectrum detection.

@@

\section{\textbf{Results}}
%Return loss measurements yields the instrument pass band response that would manifest in autocorrelation data of a single HERA element. Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$. 
Performance of the HERA feed and the dish-feed assembly has been simulated by the em solver "High Frequency Structural Simulator(HFSS)" using the finite element method. 
The simulated and measured return loss of the feed, both magnitude and phase are shown in the upper panel of the figure \ref{RL_mag_dish}. While the simulated return loss of the feed structure shows two resonant peaks around 120 and $160~MHz$, the feed resonance occur at slightly higher frequencies. Notable are the difference in the shape of the resonant peaks. While the simulated response shows very wide resonant peaks, as expected from this dipole structures, the measured return loss of the feed has a narrow peak around its low frequency resonance. This feature dominates the fall off rate in the delay response of the system bandpass. The delay response of the feed is shown in figure \ref{ds_feed_on_dish_trans}. \begin{figure*}[ht]
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_mag_feed.png}
\end{minipage}
\hspace{0.1cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_ph_feed.png}
\end{minipage}
\vspace{0.1cm}  
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_mag_dish.png}
\end{minipage}
\hspace{0.1cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_ph_HERA.png}
\end{minipage}
\caption{Upper panel: Magnitude and phase of the return loss of the feed as simulated and measured. Both measurement and simulation shows similar level of return loss across the band with marginally better return loss at the high frequency end of the band. Lower panel: Magnitude and phase of return loss when the feed is suspended at the focal point of the dish which 5~m above the dish vertex.}   
\label{RL_mag_dish}
\end{figure*}

\begin{figure}       
\centering
\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_feed_dish.png}
\caption{Delay spectrum of the HERA feed (brown) estimated by taking the Fourier transform of the measured return loss of power at the feed output (upper panel in figure \ref{RL_mag_dish}). The feed, when suspended on the dish results in a more complex return loss as shown in the lower panel of figure \ref{RL_mag_dish} and corresponding delay response is shown here in black. }
\label{ds_feed_on_dish_trans}
\end{figure}

Lower panel of the figure \ref{RL_mag_dish} shows the measured return loss when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex. The measured return loss is much more complex than what is found from the simulation. %To estimate the delay spectrum of the dish-feed assembly i.e one single HERA element, this measurement is first corrected to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}. The corrected measurement is then Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{corrected_response}. 
Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution. A number of systematic effects as well as mathematical artifacts that are critical to this measurement and their effects on the corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.

\subsection{Zero delay response}
%At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.
